Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2023-06-19 unimodular-covers-CombTheory-final.tex
new claim

We let $H_1=\{f_q(x) \leq 0\}$ and $H_2=\{f_q(x) \geq 0\}$; similarly let $V_1=\{f_p(x) \leq f_p(p)\}$ and $V_2=\{f_p(x) \geq f_p(p)\}$.%
\footnote{Since in our figures $p$ and $q$ are vertical and horizontal, we use the letters $V$ and $H$ for the half-planes they defined. Similarly, later in the proof we use the letters $b$, $t$, $r$, and $l$ for certain  points and segments meaning ``bottom'', ``top'', ``right'' and ``left''.}
%
\begin{figure}[htb]
\includegraphics[scale=.3]{setup.png}
\caption{Setup for the proof of \Cref{lemma:cayley}}
\label{fig:setup}
\end{figure}

%
Since we can perform without loss of generality respective lattice translations to $P$ and to $Q$, we assume that the segments $p$ and $q$ intersect in their relative interiors and that $f_q(p_1)=-1$. That is,
\[
-1=f_q(p_1) < 0 < f_q(p_1), \quad
-f_p(q_1) < 0 < f_p(q_2).
\]
In particular, $p$ must be in the interior of $q +\vecline p$ and $q$ in the interior of $p +\vecline q$
Our assumption also implies that $p_1$ is the unique lattice point with $f_q(x)=-1$ in $q +\vecline p$. Similarly, the unique lattice point in the strip with $f_q(x)=1$ is  $q_1+q_2 -p_1$.
See Figure~\ref{fig:setup} for an illustration of this setup.

@@

We are now ready to show a contradiction. Since the normal fan of $Q$ refines that of $P$, $Q$ must contain an edge parallel to $r$ on the right. Let $r'$ be a primitive segment along this edge, so that $r'$ is a translated copy of $r$.
 Let $r_1'$ and $r_2'$ be its endpoints.

@@

>>>>

%
Since we can perform without loss of generality respective lattice translations to $P$ and to $Q$, we assume that the segments $p$ and $q$ intersect in their relative interiors and that $f_q(p_1)=-1$. That is,
\[
-1=f_q(p_1) < 0 < f_q(p_1), \quad
-f_p(q_1) < 0 < f_p(q_2).
\]
In particular, $p$ must be in the interior of $q +\vecline p$ and $q$ in the interior of $p +\vecline q$
Our assumption also implies that $p_1$ is the unique lattice point with $f_q(x)=-1$ in $q +\vecline p$. Similarly, the unique lattice point in the strip with $f_q(x)=1$ is  $q_1+q_2 -p_1$.

Finally, we let $H_1=\{f_q(x) \leq 0\}$ and $H_2=\{f_q(x) \geq 0\}$; similarly let $V_1=\{f_p(x) \leq f_p(p)\}$ and $V_2=\{f_p(x) \geq f_p(p)\}$.%
\footnote{Since in our figures $p$ and $q$ are vertical and horizontal, we use the letters $V$ and $H$ for the half-planes they defined. Similarly, later in the proof we use the letters $b$, $t$, $r$, and $l$ for certain  points and segments meaning ``bottom'', ``top'', ``right'' and ``left''.}
See Figure~\ref{fig:setup} for an illustration of this setup.
%
\begin{figure}[htb]
\includegraphics[scale=.3]{setup.png}
\caption{Setup for the proof of \Cref{lemma:cayley}}
\label{fig:setup}
\end{figure}

@@

\begin{claim}
\label{claim:g2}
$g(r_2) - g(r_1) <1$.
\end{claim}

\begin{proof}
UNFINISHED

Since the normal fan of $Q$ refines that of $P$, $Q$ must contain an edge parallel to $r$ on the right. Let $r'$ be a primitive segment along this edge, so that $r'$ is a translated copy of $r$.
 Let $r_1'$ and $r_2'$ be its endpoints.

@@

We now have a contradiction. Claim~\ref{claim:g} says that $g(r_2) - g(r_1) >0$ and Claim~\ref{claim:g2}  that $g(r_2) - g(r_1) <1$. Since  $g(r_2) - g(r_1)$ is an integer, this is impossible.
\end{proof}
